Binary Latent Representations for Efficient Ranking

### 2017-06-13 paper/paper.tex
Offer instead of enable.

\begin{abstract}
Large-scale recommender systems often face severe latency and storage constraints at prediction time. To relax those, we train recommendation models that use binary rather than real-valued user and item representations, and show that they enable a range of attractive speed-accuracy trade-offs. In particular, we demonstrate 13 times faster prediction at the expense of a modest 4\% loss in ranking accuracy on the Movielens 100K dataset.
\end{abstract}

>>>>

\begin{abstract}
Large-scale recommender systems often face severe latency and storage constraints at prediction time. To relax those, we train recommendation models that use binary rather than real-valued user and item representations, and show that they offer a range of attractive speed-accuracy trade-offs. In particular, we demonstrate 13 times faster prediction at the expense of a modest 4\% loss in ranking accuracy on the Movielens 100K dataset.
\end{abstract}
